\huge{ \emph{Supplement to} Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}

### 2016-12-03 RA-L/theory.tex
Added the algorithm

\begin{algorithm}
\caption{GenerateDesired$x$-spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:XControl}
\begin{algorithmic}[1]
\Require knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
$(0,0)$ is bottom corner, $s_1$ is topmost robot, 
 $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
\State flag $\gets 0$
 \If {$ r_{1y}  \equiv r_{2y}$} 
\State perturb $x$ values
\State flag $\gets 1$
\EndIf
%\Ensure   $ r_{1y} - r_{2y}  \equiv s_{1y} - s_{2y} $   %$\Delta y(t) \equiv \Delta y(0)$ 
\State $\epsilon \gets $ small number
\State $ \Delta s_x  \gets r_{1x} - r_{2x} $
\State $ \Delta e_x \gets e_{1x} - e_{2x} $
\If {$\Delta e_x < 0 $ }
\State move$( L-\epsilon-\max( r_{1x},r_{2x}) ,0)   $ \Comment{Near right wall}
\Else 
\State  move$ ( \epsilon-\min( r_{1x},r_{2x}),0 )    $ \Comment{Near left wall}
\EndIf
\State move$(0, -\min( r_{1y},r_{2y} ))$ \Comment{Move to bottom}
\If {$\Delta e_x - (r_{1x} - r_{2x} ) > 0 $}
\State move$(\min(|\Delta e_x - \Delta s_x |, L- r_{1x}), 0)$  \Comment{Move right}
\Else
\State move$(-\min(|\Delta e_x - \Delta s_x |, r_{1x}), 0)$\Comment{Move left}
\EndIf 
\State move$(0, \epsilon)$ \Comment{Move up}
\If {$r_{1x} - r_{2x} \not\equiv \Delta e_x$} 
\State GenerateDesired$x$-spacing($r_1,r_2,e_1,e_2,L$)
\EndIf

 \If {$ flag == 1$} 
\State unperturb $x$ values
\EndIf

\State  \Return $(r_1,r_2)$
\end{algorithmic}
\end{algorithm}

@@

\subsection{Controlling Covariance Using Wall Friction}\label{subsec:ClosedLoopCovarianceControl}
Assume an open workspace with infinite boundary friction. Goal variances and covariance are  $(\sigma_{goalx}^2,\sigma_{goaly}^2, \sigma_{goalxy})$ and mean, variances and covariance of the swarm  are $( \bar{x},\bar{y},\sigma_x^2,\sigma_y^2, \sigma_{xy})$. 
%$\sigma_x^2$ decreases when the swarm is pushed into vertical walls, and $\sigma_y^2$ decreases when the swarm is pushed into horizontal walls. Alg.~\ref{alg:CovCont} procedes as follows:
\begin{enumerate}
\item swarm pushed into the left wall until $\sigma_x^2 \le c_1\sigma_{goalx}^2$.  
\item swarm's mean position is moved to the center of the workspace
\item swarm pushed into the bottom wall until $\sigma_y^2 \le  \sigma_{goaly}^2$. 
\item if $\sigma_{goalxy}>0$ swarm slides right until $\sigma_{xy} \ge \sigma_{goalxy}$ \\
else swarm slides left until $\sigma_{xy} \le \sigma_{goalxy}$ 
\item  swarm's mean position is moved to the center of the workspace
\end{enumerate}
The constant $c_1$ in step 1 should be less than 1 to ensure $\sigma_x^2$ stays within tolerance during the subsequent moves.

>>>>

%\begin{algorithm}
%\caption{GenerateDesired$x$-spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:XControl}
%\begin{algorithmic}[1]
%\Require knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
%$(0,0)$ is bottom corner, $s_1$ is topmost robot, 
% $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
%\State flag $\gets 0$
% \If {$ r_{1y}  \equiv r_{2y}$} 
%\State perturb $x$ values
%\State flag $\gets 1$
%\EndIf
%%\Ensure   $ r_{1y} - r_{2y}  \equiv s_{1y} - s_{2y} $   %$\Delta y(t) \equiv \Delta y(0)$ 
%\State $\epsilon \gets $ small number
%\State $ \Delta s_x  \gets r_{1x} - r_{2x} $
%\State $ \Delta e_x \gets e_{1x} - e_{2x} $
%\If {$\Delta e_x < 0 $ }
%\State move$( L-\epsilon-\max( r_{1x},r_{2x}) ,0)   $ \Comment{Near right wall}
%\Else 
%\State  move$ ( \epsilon-\min( r_{1x},r_{2x}),0 )    $ \Comment{Near left wall}
%\EndIf
%\State move$(0, -\min( r_{1y},r_{2y} ))$ \Comment{Move to bottom}
%\If {$\Delta e_x - (r_{1x} - r_{2x} ) > 0 $}
%\State move$(\min(|\Delta e_x - \Delta s_x |, L- r_{1x}), 0)$  \Comment{Move right}
%\Else
%\State move$(-\min(|\Delta e_x - \Delta s_x |, r_{1x}), 0)$\Comment{Move left}
%\EndIf 
%\State move$(0, \epsilon)$ \Comment{Move up}
%\If {$r_{1x} - r_{2x} \not\equiv \Delta e_x$} 
%\State GenerateDesired$x$-spacing($r_1,r_2,e_1,e_2,L$)
%\EndIf
%
% \If {$ flag == 1$} 
%\State unperturb $x$ values
%\EndIf
%
%\State  \Return $(r_1,r_2)$
%\end{algorithmic}
%\end{algorithm}
\begin{algorithm}
\caption{GenerateDesired spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:XControl}
\begin{algorithmic}[1]
\Require knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
$(0,0)$ is bottom corner, $s_1$ is topmost, leftmost robot, 
 $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
\State $\Delta e_y = e_2.y - e_1.y$
\State $\Delta e_x = e_2.x - e_1.x$
\If {$\Delta e_y \neq 0$}
\State $sign \gets \frac{|\Delta e_y|}{\Delta e_y}$
\Else
\State $sign \gets 0$
\EndIf
\State Move to $(-r_1.x , -\min(R_2.y , R_1.y+ \Delta e_y)+\epsilon)$
\State Move to $(-\min(|-r_2.x+ \Delta e_x|, r_2.x), sign \, \min(\max(r_1.y + \Delta e_y, r_2.y)-\epsilon,L-\epsilon)+ \epsilon)$
\If {$r_2.y \neq r_1.y$}
\State Move to $(\max(\epsilon, \Delta e_x- (r_2.x - r_1.x)), -\min(r_1.y , r_2.y))$
\State Move to $\Delta e_x , (|sign|-1) \epsilon$
\EndIf
\State Move to $(e_2.x - r_2.x, e_2.y - r_2.y)$
\end{algorithmic}
\end{algorithm}

@@

\subsection{Controlling Covariance Using Wall Friction}\label{subsec:ClosedLoopCovarianceControl}
Assume an obstacle-free, bounded workspace with infinite boundary friction. Goal variances and covariance are  $(\sigma_{goalx}^2,\sigma_{goaly}^2, \sigma_{goalxy})$ and mean, variances and covariance of the swarm  are $( \bar{x},\bar{y},\sigma_x^2,\sigma_y^2, \sigma_{xy})$. 
%$\sigma_x^2$ decreases when the swarm is pushed into vertical walls, and $\sigma_y^2$ decreases when the swarm is pushed into horizontal walls. Alg.~\ref{alg:CovCont} procedes as follows:
\begin{enumerate}
\item swarm pushed into the left wall until $\sigma_x^2 \le c_1\sigma_{goalx}^2$.  
\item swarm's mean position is moved to the center of the workspace
\item swarm pushed into the bottom wall until $\sigma_y^2 \le  \sigma_{goaly}^2$. 
\item if $\sigma_{goalxy}>0$ swarm slides right until $\sigma_{xy} \ge \sigma_{goalxy}$ \\
else swarm slides left until $\sigma_{xy} \le \sigma_{goalxy}$ 
\item  swarm's mean position is moved to the center of the workspace
\end{enumerate}
The constant $c_1$ in step 1 should be less than 1 to ensure $\sigma_x^2$ stays within tolerance during the subsequent moves.
